---
name: First
surname: Last
position: "Your Role or Career Focus"
phone: +1 (XXX) XXX-XXXX
www: yourwebsite.com
email: "you@example.com"
github: your-github
linkedin: your-linkedin
date: "`r format(Sys.time(), '%B %Y')`"
output: 
  vitae::latexcv:
    theme: classic
header-includes:
   - \usepackage{enumitem}
   - \setlist[itemize]{nosep, left=0pt}
   - \setlist[enumerate]{nosep, left=0pt}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

if (!requireNamespace(c("tinytex","vitae","tibble"), quietly = TRUE)) {
  install.packages(c("tinytex","vitae","tibble"))
}

if (Sys.which("pdflatex") == "" && !tinytex::is_tinytex()) {                    
  message("► TinyTeX not found – installing")
  tinytex::install_tinytex()        
} else {
  message("✓ LaTeX present – no installation needed.")
}

library(vitae)
library(tibble)
```

# Professional Summary

Motivated and detail-oriented marketing and analytics professional with a strong background in data interpretation, campaign strategy, and digital tools. Skilled in turning insights into action and communicating value across business teams.

# Technical Skills

- **Programming Languages:** R, Python, SQL, etc.  
- **Web Technologies:** HTML, CSS/SCSS, Quarto, CMS, Google Analytics, etc.

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ College, ~ Institution,
  "Master of [Your Field]", "20XX – Expected Graduation 20XX", "[Your School or Department]", "[Your University]",
  "Bachelor of [Your Field]", "20XX – 20XX", "[Your School or Department]", "[Your University]"
) %>%
  detailed_entries(Degree, Year, College, Institution)
```

# Work Experience

```{r}
tribble(
  ~ Years, ~ Company, ~ Duties, ~ Title,

  "Month YYYY – Month YYYY", "Company or Organization Name",
  list(
    "Summarize responsibility or achievement \\#1.",
    "Highlight tools, technologies, or methods used.",
    "Mention metrics, goals, or impact if possible.",
    "Add communication or leadership responsibilities here."
  ),
  "Job Title",

  "Month YYYY – Month YYYY", "Another Company or Team",
  list(
    "Led a project or team focused on [insert focus].",
    "Collaborated cross-functionally with [departments/roles].",
    "Managed content, campaigns, or dashboards.",
    "Contributed to strategic planning or reporting."
  ),
  "Job Title"

) %>%
  detailed_entries(
    what = Title,
    when = Years,
    with = Company,
    why = Duties
  )
```